### 2021-04-19 main.tex
Resolve R1 comment: Relate your work to ENIGMA

In \cite{Olsak2019} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
They use the \glspl{gnn} to solve classification tasks such as premise selection.
While our system is trained on a proxy classification task,
the main task it is evaluated on is the generation of useful precedences.

@@

\todo[inline,author=R1]{An obvious question is how is this work related to the work and methods
used for Enigma?

Although the paper related to the Enigma system by Jakubuv has been
cited, it appears to not be referred to in the text. It should be referred and
the reference list should be checked.
}

>>>>

In \cite{Olsak2019}, \cite{Jakubuv2020} and \cite{Rawson2020}, the authors propose similar \gls{gnn} architectures to solve tasks on \gls{fol} problems.
They use the \glspl{gnn} to solve classification tasks such as premise selection.
While our system is trained on a proxy classification task,
the main task it is evaluated on is the generation of useful precedences.
% Jakubuv2020 uses the same architecture as Olsak2019.
% Our GNN uses a different particular architecture than Olsak2019.

@@
